\documentclass[a4paper]{report}

%opening
\title{Constitution of Awesomeland}
\author{}

\begin{document}

\maketitle

\begin{abstract}
	
	Executive is corporation sole, can exercise power within currently enacted laws and bill of rights.
	
	Legislature is council who decide on policy, 
	
	You cannot have a monarchy with unabsolute power. Either they are above the law, or they are under it.
	If the monarch has to abide by the law, they do not have absolute power, and are thus not a monarch.
	
	Sovereignty
	Military and it's head

\end{abstract}

\chapter{The Parliament}

\section{Test}

Role of parliament is not to action things, but to make laws.

The parliament is to have two houses. One will have members chosen by area (all electorates the same physical size), one will have members chosen by population (all electorates the same population).

All laws expire after a period of 50 years from being passed. They must be re-passed before they expire if they are to continue being active.


\subsection{Cannot make laws that go back in time}

\chapter{The Executive Government}

\subsection{The Head of Government}
The Head of Government is the ceremonial head of the government and represents the power of the government in the nation. 

The Head of Government cannot be a former council or parliament member. The Head of Government acts on the advice of the council. 

The HoG can kick of either the council or the parliament or both. The council unaminously can get rid of the HoG. 

HoG terms are for five years and the HoG is voted on by the council. 

Powers given to the HoG exclusively:

\begin{itemize}
	\item To preside over meetings of the council.
	\item To dismiss individual members of the council.
	\item To dismiss the parliament.
	\item To appoint and dismiss judges.
\end{itemize}

\subsection{The Council}
The Council is responsible for exercising the power of the government within the bounds of this constitution and within the laws of the day. Majority vote is good for decisions. The council members are voted on individually for single positions within the council by all citizens of the state. Council terms are for two years and are made on a rotating basis. The councillors are as follows:
* Treasury and Taxation
* Judiciary Matters
* Foreign Matters

\chapter{The Judicature}

Judge terms limited to 15 years with no renewal.

\section{Appeals and Investigations Court}

This is the highest court and hears appeals from the Higher Court, constitutional challenges, as well as performing special investigations into other areas of the government (such as the police force or parliament). Impeachment hearings.

A motion passed by both houses of parliament is required to begin a special investigation within a particular scope.

A special investigation can force anybody to give evidence regarding that scope, and criminal charges can be laid depending on that evidence.

A panel of 5 judges will preside over any proceedings.

\section{Higher Court}

* Judge + Jury(10)

Hears the following crimes:

* Crimes against the person (such as murder or rape).

* Crimes against the state (such as treason).

* Crimes which involve the bill of rights.

* Hears crimes against the person, crimes against the state (such as treason), and 

* Sees murder, treason, and torts for amounts larger than X. Anything which is against the bill of rights.

\section{Lower Court}

* Judge

\chapter{Miscellaneous}

\section{Bill Of Rights}

All natural persons falling under the jurisdiction of The Country have the 
following irrevocable rights:

\subsection{Freedom from Discrimination}

These rights apply equally to all ages, sexes, religions and races.

\subsection{Right to Free Speech}

Free speech, except racism/sexist with no base.

\subsection{Right to Privacy}

Privacy, except under warrant.

\subsection{Double Jeopardy}

\section{Divisions of Government}

Any person who is a member of any one branch of government cannot be a member of any other branch of government. Only citizens can hold positions in the government.

\section{Election of People}

\section{Warfare}

The president may call up an army.

Wars must be voted on every six months by the parliament. 12 after a no vote, all troops must be home.

Universal National Service:
22. Create a Constitutional requirement that all able-bodied young Americans devote at least 2 years of their lives in service to the country.and whether the service is civilian or military, domestic or foreign, would be up to each individual. The civilian, military, and nonprofit options would have to accommodate the varied talents of the population, as well as our diverse dictates of conscience. 

\section{Misc.}

Money must be a real object. No fiat currencies.

Legal tender is gold and silver bullion.
Pure gold and silver from anywhere can be used.
The government is allowed to offer minting services.

The government cannot borrow money.

The government is allowed to tax citizens in order to pay for things.

Voting is done by every citizen of the country over the age of twenty. Voting is non-compulsory.
KNIGHTHOODS

Only natural persons may donate to political persons or to political parties.

\section{Changes to the Constitution}

the people have the right of resistance as a last resort against any attempt to abolish the constitutional order.



Legislative Council - voted in individually, in two houses.
Executive - voted in as a team.
Judiciary Council - a pool of judges from which things are heard. selected by judges in higher courts. judges in supreme court are allocated by audit tribunal.

An audit tribunal can be come invented by two of the seperate powers acting together (ie, a vote by the legislature and a majority of judges) to investigate the third. 3 investigators is brought in from each branch, making 9 investigators. They can make recommendations, as well as have the power to dismiss the executive, individual legislative council members, or judges by a two-thirds majority of investigators.

Electoral commission? After a post is vacated (term is up or kicked out) then the electoral commission will hold a vote for the new people.

Changing the constitution?


\end{document}
